---
title: "ST&Cont3 Results"
author: "Lisa M. Huang"
date: "March 28, 2018"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include = FALSE}
#Load the following data tables from the full analyses into the global environment:
load(file = "demogW.rda")
```


```{r include = FALSE}
setwd("C:/Users/Lisa/Documents/Lisa/Experiments/Stereotyping in context/ST&Context3/r markdown")
getwd()
```


## Contents

1. Study Design

2. Demographics
    + Sample size
    + Age
    + Ethnicity
    + Gender  

3. Chi-square tests
    + Congruent context
    + Incongruent context
    + Shared context
    + Mixed context
    + All context  

4. Moderation by Stereotype
    + Congruent context
    + Incongruent context  

5. Scale ratings
    + Means
    + Standard deviations
    + Analysis 
    + Bar graph



## 1. Study Design

### *Variables*

* Stereotype (between-subjects)
    + Extraverted
    + Introverted
    
* Context (within-subjects)
    + Congruent
    + Incongruent
    + Shared
    + Mixed
    + Novel
    + All

### *Sample size*

```{r echo = FALSE}
stpCount <- table(demogW$stereotype)
stpProp <- prop.table(table(demogW$stereotype))
cbind(stpCount,stpProp)
```

Stereotype    | Counts        | Percentages
------------- | ------------- | -------------
extraverted   | 140           | 54.9%
introverted   | 115           | 45.1%



## 2. Demographics

### *Age*

```{r echo = FALSE}
cat("Mean: ", mean(demogW$dage) )
cat("Standard Deviation: ", sd(demogW$dage) )
```

### *Ethnicity*

```{r echo = FALSE}
ethnicCount <- table(demogW$dethnic)
ethnicProp <- prop.table(table(demogW$dethnic))
cbind(ethnicCount,ethnicProp)
```

### *Gender*

```{r echo = FALSE}
genderCount <- table(demogW$dgender)
genderProp <- prop.table(table(demogW$dgender))
cbind(genderCount,genderProp)
```



## 3. Chi-square tests

```{r include = FALSE}
#Function for effect size
cohenW = function(chisq, n) {
  w = (sqrt(chisq/n))
  return(w)
}

#Title of counts and proportions
label <- 'Counts and proportions'
```


### *Congruent context*

```{r echo = FALSE}
load(file = "testCons.rda")

label
consCt <- table(testCons$response3)   
consProp <- prop.table(table(testCons$response3))   
rbind(consCt, consProp)

cons <- c(465,45)              
exp <- c(.5,.5)
chisq.test(cons, p=exp)

cat("Cohen's W: ", cohenW(345.88,510) )
```

### *Incongruent context*

```{r echo = FALSE}
load(file = "testIncs.rda")

label
incsCt <- table(testIncs$response3)
incsProp <- prop.table(table(testIncs$response3)) 
rbind(incsCt, incsProp)

incs <- c(42,468)   
exp <- c(.5,.5)
chisq.test(incs, p=exp)

cat("Cohen's W: ", cohenW(355.84,510) )

```

### *Shared context*

```{r echo = FALSE}
load(file = "testShared.rda")

label
shrdCt <- table(testShared$response3)
shrdProp <- prop.table(table(testShared$response3)) 
rbind(shrdCt, shrdProp)

shrd <- c(566,454)   
exp <- c(.5,.5)
chisq.test(shrd, p=exp)

cat("Cohen's W: ", cohenW(12.298,1020) )
```

### *Mixed context*

```{r echo = FALSE}
load(file = "testMixed.rda")

label
mixCt <- table(testMixed$response3)
mixProp <- prop.table(table(testMixed$response3)) 
rbind(mixCt, mixProp)

mix <- c(502,518)   
exp <- c(.5,.5)
chisq.test(mix, p=exp)

cat("Cohen's W: ", cohenW(.25098,1020) )
```

### *Novel context*

```{r echo = FALSE}
load(file = "testNovel.rda")

label
novCt <- table(testNovel$response3)
novProp <- prop.table(table(testNovel$response3)) 
rbind(novCt, novProp)

nov <- c(650,370)   
exp <- c(.5,.5)
chisq.test(nov, p=exp)

cat("Cohen's W: ", cohenW(76.863,1020) )
```

### *All context*

```{r echo = FALSE}
load(file = "testAll.rda")

label
allCt <- table(testAll$response3)
allProp <- prop.table(table(testAll$response3)) 
rbind(allCt, allProp)

all <- c(490,530)   
exp <- c(.5,.5)
chisq.test(all, p=exp)

cat("Cohen's W: ", cohenW(1.5686,1020) )
```



## 4. Moderation by Stereotype

```{r include = FALSE}
library(gmodels)
```

### *Congruent context*

```{r echo = FALSE}
CrossTable(testCons$stereotype, testCons$response3, fisher = T, chisq = T, expected = T, 
           prop.c = F, prop.t = F, sresid = T, format = "SPSS")

cat("Cohen's W: ", cohenW(0.7207373, 510) )
```

### *Incongruent context*

```{r echo = FALSE}
CrossTable(testIncs$stereotype, testIncs$response3, fisher = T, chisq = T, expected = T, 
           prop.c = F, prop.t = F, sresid = T, format = "SPSS")

cat("Cohen's W: ", cohenW(3.846858, 510) )
```


## 5. Scale Ratings

```{r include = FALSE}
library(dplyr)
scaleMainW <- read.csv("scaleMainW.csv", header = TRUE)
```

### *Means, by stereotype and context*

```{r echo = FALSE}
aggregate(scaleMainW[c("Pcons","Pincs","shared","mixed","novel","overall")], 
          scaleMainW["stereotype"], mean, na.rm=TRUE)
```

### *Standard Deviations, by stereotype and context*

```{r echo = FALSE}
aggregate(scaleMainW[c("Pcons","Pincs","shared","mixed","novel","overall")], 
          scaleMainW["stereotype"], sd, na.rm=TRUE)
```

### *Analysis*

```{r echo = FALSE}
load(file = "scaleMain.rda")
library(ez)   #For the ANOVA

mixedAOV <- ezANOVA(data = scaleMain, 
                    dv = .(response), 
                    wid = .(subject), 
                    within = .(trialType), 
                    between = .(stereotype), 
                    type = 3, 
                    detailed = TRUE,
                    return_aov = TRUE)

mixedAOV

print("Effect Sizes - partial eta squared")

eta2p = function(eff, err) {
  y = eff/(eff + err)
  return(y)
}

#trialType (i.e., context)
cat("Context: ", eta2p(112.1569, 3115.2833)) 

#stereotype
cat("Stereotype: ", eta2p(92.5419, 491.1444)) 

#trialType x stereotype

cat("Context x Stereotype: ", eta2p(2153.2265, 3115.2833) )
```


### *Bar Graph of scale ratings*

```{r include = FALSE}
library(ggplot2)
```

```{r echo = FALSE, fig.width = 7, fig.height = 5}
ggplot(scaleMain, aes(trialType, response, fill = stereotype)) +
  stat_summary(fun.y = mean, geom = 'bar', position = 'dodge') +
  labs(x = 'Context', y = 'extraversion/introversion rating') +
  scale_x_discrete(limits = c('Pcons','Pincs','novel','shared','mixed','overall')) 
```


